Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-24 paper/paper.tex
table 3 values

\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \centering
  \begin{tabular}{lcrp{9cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{\#~Options Seed Rule} &
    \multicolumn{1}{c}{Rank} \\
    \midrule
    Ping Scan & 5 & - \\
    SYN Flood & - & - \\
    JBoss JMX & - & 23 \\
    WeBid & - & -\\    
    ColdFusion & - & 5\\
    .htaccess access & - & 2\\
    .idq access & - & 2 \\
    iisadmin access & - & 1 \\
    /system32/ in URI & - & 2 \\
    Script tag in URI & - & - \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \centering
  \begin{tabular}{lcrp{9cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{\#~Options Seed Rule} &
    \multicolumn{1}{c}{Rank} \\
    \midrule
    Ping Scan & 5 & - \\
    SYN Flood & 2 & - \\
    JBoss JMX & 23 & 23 \\
    WeBid & 23 & -\\    
    ColdFusion & 19 & 5\\
    .htaccess access & 17 & 2\\
    .idq access & 19 & 2 \\
    iisadmin access & 17 & 1 \\
    /system32/ in URI & 20 & 2 \\
    Script tag in URI & 22 & - \\
    \bottomrule
  \end{tabular}
\end{table}
